% laTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 

\begin{document} 

\name{Jai C. Dhyani\\[12pt]}     % the \\[12pt] adds a blank
				        % line after name      

\address{   6210 Belcrest Road \#1217 \\ 
            Hyattsville, MD 20782 \\ 
            jai@jaibot.com \\ 
            (609) 948-4264 \\ 
            http://jaibot.com \\ 
            http://github.com/jaibot }

\address{}
                                  
\begin{resume}

\section{EDUCATION}          
    University of Chicago, B.A. in Computer Science 2010  \\   
    Concentration in Artificial Intelligence      
 
\section{EXPERIENCE}
   \vspace{-0.1in}	
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Chief Technology Officer} \>Appliance Builders Wholesalers \> ~~~~~~ Summer 2008 \\
                             \>Silver Spring, MD                    \> ~~~~~~ to Present
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    Managed all IT-related responsibilities for a small company undergoing significant infrastructure changes. Responsibilities ranged from low-level troubleshooting to network engineering and multiplatform system administration. Managed 50+ users across 4 different locations.
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Research Assistant} \>University of Chicago \> ~~~~~~ Summer 2007\\
                          \>Chicago, IL
   \end{tabbing}\vspace{-20pt}
   Investigated tonal levels in synthesized speech, and methods of algorithmic pitch correction
   in speech.
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Database Programmer } \>University of Chicago Admissions Office \> ~~~~~~ Spring 2007\\
                             \>Chicago, IL
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
   Created web interfaces for querying database of applicants and interviewers to simplify admissions and the process of assigning alumni to applicants for interviews.
   \begin{tabbing}%
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions          
   {\bf Research Assistant}  \>Rutgers DIMACS \> ~~~~~~ Summer 2006\\
                          \>East Brunswick, NJ
   \end{tabbing}\vspace{-20pt}
   Investigated use of Support Vector Machines on EKG readings to predict seizure onset times.
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf IT Assistant} \>Montgomery Home Title \> ~~~~~~ Summer 2004, 2005\\
                             \>Rockville, MD
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
   Assisted day-to-day IT and administration responsibilities for a medium-sized company with offices across the country in a Windows-centric environment. 


\section{COMPUTER SKILLS}          
    Extremely proficient Python programmer. \\
    Familiar with Unix (esp. Debian Linux), Windows, OS X.\\
    Four years experience in LAMP server environments (esp. personal web server)\\
    Over a decade of providing end-user technical support \\
    Experience in academic artificial intelligence, especially Support Vector Machines \\
    Miscellaneous experience with: C, C++, Java, Lisp/Scheme, PHP, HTML, CSS, SQL (MySQL, PostgreSQL, Microsoft SQL Server), \LaTeX \\
    Semi-fanatical Vim user (but some of my best friends use emacs!)

 
\section{EXTRACURRICULAR ACTIVITIES and COMPETITIONS}
    Google Code Jam, 2010 as confused.is.good - Top 2000 Worldwide \\
    Project Euler, ongoing - code and rank available at github \\
    ICPC 2007 - University of Chicago, team ``Works in Theory`` \\
    Treasurer, University of Chicago ACM 2007-2009 \\         
    Member, City of Chicago ACM 2007-2009
 
\end{resume}
\end{document}
